---
title: "Cookbook Project"
Author: "François Lefebvre"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme:
      version: 4
      bootswatch: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(htmltools)
```



```{r eval=FALSE, include=FALSE}
# source: https://pkgs.rstudio.com/flexdashboard/articles/using.html
# themes available
c("cerulean", "cosmo", "cyborg", "darkly", "flatly", "journal", "litera", "lumen", "lux", "materia", "minty", "pulse", "sandstone", "simplex", "sketchy", "slate", "solar", "spacelab", "superhero", "united", "yeti")
# favorites
c("journal", "superhero", "united", "darkly", "yeti", "materia", "cerulean", "sandstone", "slate", "simplex", "cosmo")
```



Comments
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### <font size="5" color = "darkblue"><em>Decision Support</em></font>

<font size="7" color = "goldenrod">

* Trends by business groups
* Profit: Added value vs raw pricing
* Sales Analysis <u>before</u> cost analysis

</font>


### <font size="5" color = "darkblue"><em>Transactions</em></font>

<font size="7" color = "steelblue">

* Pattern of empty transactions
  - Fit the hurdle model
  - Identify the loss leaders, i.e. predictors of losses
* Pattern of sales returns and other negative transactions
* Estimate the cost per transaction document
  - Compute the ideal volume discount/premium

</font>


### <font size="5" color = "darkblue"><em>Business Groups</em></font>

<font size="7" color = "steelblue">

* Identify the business groups of clients and products
  - Explain at least 70% of variance
  - Maximum 3 business groups usually enough
  - Evaluate feasibility of using the groups in the system


</font>

### <font size="5" color = "darkblue"><em>Pricing</em></font>

<font size="7" color = "steelblue">

* **Added value vs raw pricing **
* Denominator: Units vs amounts

</font>


</font>

### <font size="5" color = "darkblue"><em>Definition</em></font>

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

$$
\begin{align*}
\underbrace{\frac{Profit}{Capital}}_{\text{ROI}} &= 
\underbrace{\frac{Profit}{Sales}}_{\text{Profit Margin}} \times 
\underbrace{\frac{Sales}{Capital}}_{\text{Turnover}} \\ \\ \\
\text{also, same idea, with production data} \\ \\ \\
\underbrace{\frac{Added\;Value}{Capital}}_{\text{ROI}} &= 
\underbrace{\frac{Added\;Value}{Hours}}_{\text{Price}} \times 
\underbrace{\frac{Hours}{Capital}}_{\text{Turnover}} 
\end{align*}
$$



ROI Value
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------


### <font color = "blueviolet">**ROI Map - Added Value**</font>

```{r}
# a_file <- here::here("reports", "data", "groups_roi_addval.png")
# knitr::include_graphics(path = a_file)
a_file <- here::here("reports", "data", "ply_groups_roi_addval.qs")
# infoRDS(a_file)
stopifnot(file.exists(a_file))
qs::qread(file = a_file)
```


Column {data-width=350}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
a_file <- here::here("reports", "data", "gt_groups_roi.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```



ROI Profit
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------


### <font color = "blueviolet">**ROI Map - Profit**</font>

```{r}
# a_file <- here::here("reports", "data", "groups_roi_profit.png")
# knitr::include_graphics(path = a_file)
a_file <- here::here("reports", "data", "ply_groups_roi_profit.qs")
# infoRDS(a_file)
stopifnot(file.exists(a_file))
qs::qread(file = a_file)
```


Column {data-width=350}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
a_file <- here::here("reports", "data", "gt_groups_roi.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```


Price of Material
=======================================================================


Column {data-width=700}
-----------------------------------------------------------------------

### <font color = "blueviolet">**Price per Dollar of Material**</font>


```{r out.width = '90%'}
a_file <- here::here("reports", "data", "ggp_sales2mat_box.png")
knitr::include_graphics(path = a_file)
```



Column {data-width=300}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_groups_ratios.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```


Price of Hour 
=======================================================================


Column {data-width=700}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Price per Hour**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_addval2hrs_box.png")
knitr::include_graphics(path = a_file)
```


Column {data-width=300}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_groups_ratios.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```



Price of Material Dist
=======================================================================


Column {data-width=700}
-----------------------------------------------------------------------

### <font color = "blueviolet">**Price per material distribution**</font>


```{r}
a_file <- here::here("reports", "data", "ggp_dist_nice_mat.png")
knitr::include_graphics(path = a_file)
```



Column {data-width=300}
-----------------------------------------------------------------------

### <font color = "blueviolet">**Table of Variable Costs**</font>


```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_intrvl.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```



Price of Hours Dist
=======================================================================


Column {data-width=700}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Price per hour distribution**</font>


```{r}
a_file <- here::here("reports", "data", "ggp_dist_nice_hrs.png")
knitr::include_graphics(path = a_file)
```


Column {data-width=300}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Table of Variable Costs**</font>


```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_intrvl.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```



Non Compliances Tree
=======================================================================

Column {data-width=700}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Non-Compliance Tree**</font>


```{r out.width = '90%'}
a_file <- here::here("reports", "data", "ggp_noncompl_tree.png")
knitr::include_graphics(path = a_file)
```

Column {data-width=300}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>

### <font color = "blueviolet">**Table of Non Compliances**</font>


```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_noncompl.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```



Non Compliances
=======================================================================

Column {data-width=700}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Non-Compliance Histogram**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_noncompl_hist.png")
knitr::include_graphics(path = a_file)
```

Column {data-width=300}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>


### <font color = "blueviolet">**Table of Non Compliances**</font>


```{r}
# get the gt table
a_file <- here::here("reports", "data", "gt_noncompl.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```


Clean Value
=======================================================================


Column {data-width=1000}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Sales vs Material**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_valid_clean_addval.png")
knitr::include_graphics(path = a_file)
```


Clean Price
=======================================================================


Column {data-width=1000}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Added Value vs Hours**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_valid_clean_price.png")
knitr::include_graphics(path = a_file)
```



Valid 3D
=======================================================================


Column {data-width=700}
-----------------------------------------------------------------------



### <font color = "blueviolet">**Raw Data 3D**</font>


```{r}
a_file <- here::here("reports", "data", "ply_valid_3D.qs")
# infoRDS(a_file)
stopifnot(file.exists(a_file))
qs::qread(file = a_file)
```


Column {data-width=300}
-----------------------------------------------------------------------

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

### <font color = "blueviolet">**Data Summary**</font>


```{r}
a_file <- here::here("reports", "data", "gt_groups_amt.html")
stopifnot(file.exists(a_file))
htmltools::includeHTML(path = a_file)
```





Valid 2D
=======================================================================


Column {data-width=500}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Sales vs Material**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_valid_addval.png")
knitr::include_graphics(path = a_file)
```


Column {data-width=500}
-----------------------------------------------------------------------


### <font color = "blueviolet">**Added Value vs Hrs**</font>

```{r}
a_file <- here::here("reports", "data", "ggp_valid_price.png")
knitr::include_graphics(path = a_file)
```


